---
title: "Lab 01 - Hello R"
author: "Robert Link"
date: "07/05/2021"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

The `datasaurus_dozen` file contains 1846 rows and 3 columns.

The three variables are: `dataset`,`x-values`, and `y-values`.

### Exercise 2

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=3}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```


### Exercise 3

We would also like to plot the data in the star dataset:

```{r plot-star, fig.height=3, fig.width=3}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And as before, we calculate the correlation between `x` and `y` in this dataset:

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

### Exercise 4

Now we do the exact same thing to the circle dataset.

```{r plot-circle, fig.height=3, fig.width=3}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```
Notice now that the correlations are not identical, but are reasonably close for the three data sets explored: `dino`, `star`, and `circle`.

### Exercise 5

Now we plot all 13 datasets.

```{r plot-all}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 5) +
  theme(legend.position = "none")
```

And we produce all correlations.

```{r cor-all}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```